\phatraid, yo

### 2014-05-16 paper/paper.tex
Some wording mods and bug fixes for the paper.

Distributed file stores, like Google's \chubby{}\cite{burrows-chubby}
and CS260r's \phat{}\cite{class}, send all files through a single
master node which consistently replicates the file on many slaves. In
this scheme, the master node's throughput is a bottleneck for storing
large files. We present \phatraid{} which mitigates this bottleneck by
partitioning files across many \paxos{} groups which form a \raid{}\cite{raid}
group.

@@

Google's \chubby{}\cite{burrows-chubby} is a distributed file system which
achieves consensus in the face of limited failures. Unfortunately, for storing
large files disk latency on the cluster nodes is a bottleneck. We propose
building a RAID (Redundant Array of Inexpensive Disks)\cite{raid} group out of distributed file system clusters. Large files are
sharded and disk latency is reduced proportional to number of clusters. Failure
resiliency is not completely sacrificed and we provide an analysis of the
new failure modes.

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{Store.png}
  \caption{Scatter Plot of Various \phatraidcf{$C$}{$f$} Configurations}
  \label{fig:plot}
\end{figure}

We evaluated a prototype \phatraidcf{$C$}{$f$} implementation. We simulated disk
latency with sleeps. All experiments are run on a 2013-model MacBook Pro with
8GB of RAM, and a 3GHz Intel Core i7. We found that latency scales asp
$\frac{1}{C-1}$. This is the expected behavior for breaking a file into $C-1$
chunks. We always use one bit of party.

>>>>

Distributed file stores, like Google's \chubby{}\cite{burrows-chubby}
and CS260r's \phat{}\cite{class}, send all files through a single
master node which consistently replicates the file on many slaves. In
this scheme, the master node's throughput is a bottleneck for storing
large files. We present \phatraid{} which mitigates this bottleneck by
partitioning files across many \paxos{} groups which form a \raid{1}
group.

@@

Google's \chubby{}\cite{burrows-chubby} is a distributed file system which
achieves consensus in the face of limited failures. Unfortunately, for storing
large files disk latency on the cluster nodes is a bottleneck. We propose
building a RAID group out of distributed file system clusters. Large files are
sharded and disk latency is reduced proportional to number of clusters. Failure
resiliency is not completely sacrificed and we provide an analysis of the
new failure modes.

@@

\begin{figure}
  \includegraphics[scale=0.45]{Store.pdf}
  \caption{Scatter Plot of Various \phatraidcf{$C$}{$f$} Configurations}
  \label{fig:plot}
\end{figure}

We evaluated a prototype \phatraidcf{$C$}{$f$} implementation. We simulated disk
latency with sleeps. All experiments are run on a 2013-model MacBook Pro with
8GB of RAM, and a 3GHz Intel Core i7. We found that latency scales as
$\frac{1}{C-1}$. This is the expected behavior for breaking a file into $C-1$
chunks. We always use one bit of party.
